SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-17 paper/related.tex
added
related-work

Again about two pages long

\begin{itemize}
\item \mukund{Detailed BIO motivation}
\item \srivas{Detailed BIO to Graph problem}
\end{itemize}

The following terms must be defined  in this section

\begin{itemize}
\item 3 connected
\item  ....
\end{itemize}

>>>>

\ankit{related work: other SAT works related to bio; Graph problems; Models of VTS/GRN}
\begin{enumerate}
\item Reasoning over Biological Networks using Maximum Satisfiability.
\item BioGraphE: high-performance bionetwork analysis using the Biological Graph Environment.
\item Generalized k-ary tanglegrams on level graphs: A satisfiability-based approach and its evaluation.
\item Faster than classical quantum algorithm for dense formulas of exact
satisfiability and occupation problems.
\item Model Checking Gene Regulatory Networks.
\item SMT-Based Analysis of Biological Computation.
\item A SAT-based algorithm for finding attractors in synchronous Boolean networks.
\item ILP/SMT-Based Method for Design of Boolean Networks Based on Singleton Attractors.
\item Efficient parameter search for qualitative models of regulatory networks using symbolic model checking.
\end{enumerate}
Who will do the related work?
